---
title: "Lab 00 - Hello IDS!"
author: "Loliett Valdes-Castillo"
date: "25.09.2026///"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Tibble Function

```{r}
help(tibble)
```

### Tibble example

```{r}
tib <- tibble(a = c(1,2,3), b = c(4,5,6), c = c(7,8,9))
tib
```

### Data frame example

```{r}
my_df <- data.frame(a = c(1,2,3), b = c(4,5,6), c = c(7,8,9))
my_df
```

### Class function

```{r}
class(tib)
class(my_df)
```

### What is the main difference between these two outcomes ?

tibble: "tbl_df"(tibble object); "tbl" (tidyverse tibble object) "data.frame" (data frame object) data.frame: only one class (data.frame)

### Edit the “tibble” in the first R code chunk with data collected from your team members. Ask each member:

-   What is your name?

-   What is your GitHub username?

-   What is your favourite colour?

-   What is your hobby?

-   What is your favourite number between 1 and 10.

The first row of the first row has already been completed as an example.

## Choosing a number randomly

```{r}
sample(10, size = 1)
```

## Palettes

```{r}
colours()
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Peter Rabbit", "Alice", "Flopsy", "Lily", "Max"),
  github_username = c("mcgregors-garden", "alice-garden", "flopsy-garden", 
                      "lily-garden", "max-garden"), 
  colour = c("powderblue", "blueviolet", "darkgreen", "deeppink3", "darkred"),
  hobby = c("Hopping", "Hiking", "Yoga", "Photography", "Writing"),
  favourite_number = c(2, 4, 9, 3, NA))

team_data
```

### Exercise 18

We now work on visualising our data.

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour)) +
   geom_col() +
   scale_fill_identity()
p1
```
